
\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, xcolor, geometry, enumitem, multicol, tcolorbox}

\definecolor{mainblue}{RGB}{0, 102, 204}
\geometry{a4paper, margin=1.2cm, top=1cm, bottom=3cm, footskip=1.2cm}

\begin{document}
\enlargethispage{2.5cm}

% Modern Header
\begin{tcolorbox}[colback=mainblue!5, colframe=mainblue, sharp corners, boxrule=0.5pt]
    \small \textbf{Unit:} Unit 0: Foundations of Algebra \hfill \textbf{Name:} \rule{3cm}{0.4pt} \\
    \small \textbf{Topic:} Place Value \hfill \textbf{Date:} \rule{2cm}{0.4pt} \\
    \centering \textbf{\large Advanced (Carolina Reaper)}
\end{tcolorbox}

\vspace{0.2cm}

% MCQ Section
\begin{multicols}{2}
\begin{enumerate}[label=\textbf{Q\arabic*.}, leftmargin=*, itemsep=6pt, parsep=0pt]

  \item \small The $4$ in $456$ represents $4 \times 10^$
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item 0
    \item 1
    \item 2
    \item 3
    \item 4
  \end{enumerate}

  \item \small Rounding $547$ to the nearest ten gives $$
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item 500
    \item 540
    \item 550
    \item 560
    \item 600
  \end{enumerate}

  \item \small What is the expanded form of $234$?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item $2 \cdot 10^0 + 3 \cdot 10^1 + 4 \cdot 10^2$
    \item $2 \cdot 10^2 + 3 \cdot 10^1 + 4 \cdot 10^0$
    \item $2 \cdot 10^1 + 3 \cdot 10^2 + 4 \cdot 10^0$
    \item $2 \cdot 10^0 + 3 \cdot 10^2 + 4 \cdot 10^1$
    \item $4 \cdot 10^2 + 3 \cdot 10^1 + 2 \cdot 10^0$
  \end{enumerate}

  \item \small The time $9:45$ can be represented as $9 \cdot 60^1 + 45 \cdot 60^0$ minutes. What is the value of $9:45$ in just minutes?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item 564
    \item 585
    \item 605
    \item 625
    \item 645
  \end{enumerate}

  \item \small The area of a rectangular garden is $2400$ square feet. If its length is $60$ feet, what is its width in feet?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item 20
    \item 30
    \item 40
    \item 50
    \item 60
  \end{enumerate}

  \item \small The largest 4-digit number that can be formed using the digits $1$, $2$, $3$, and $4$ without repetition is $$
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item 1234
    \item 1243
    \item 1324
    \item 3214
    \item 4321
  \end{enumerate}

  \item \small If a water tank can hold $4320$ gallons of water and $2135$ gallons are already filled, what percentage of the tank is filled?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item 40\%
    \item 45\%
    \item 49\%
    \item 50\%
    \item 55\%
  \end{enumerate}

  \item \small A bakery sells a total of $2547$ loaves of bread per day. They sell a combination of whole wheat and white bread. If they sell $1473$ whole wheat loaves, how many white bread loaves do they sell?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item 1000
    \item 1050
    \item 1074
    \item 1100
    \item 1105
  \end{enumerate}

\end{enumerate}
\end{multicols}

\vspace{-0.2cm}
\hrule
\vspace{0.2cm}
\textbf{\small Open Ended Questions (FRQ)}
\begin{enumerate}[label=\textbf{Q\arabic*.}, start=9, itemsep=5pt, topsep=0pt]

  \item \small Write the number $945$ in expanded form. Then round $945$ to the nearest hundred. \vspace{2cm}

  \item \small A person wants to buy a book that costs \$25 and a toy that costs \$17. If they have \$42, how much more money do they need to buy both items? \vspace{2cm}

\end{enumerate}

\vfill

% Chef's Tips Footer
\begin{tcolorbox}[colback=blue!5, colframe=mainblue!50, title=\small \textbf{Chef's Tips}, fonttitle=\bfseries, bottom=1mm]
\begin{itemize}[noitemsep, topsep=2pt, leftmargin=0.5cm]
  \item \scriptsize Chef's Tips: Make sure students understand the concept of place value and how it applies to various real-life scenarios.\item \scriptsize Chef's Tips: Remind students to read the questions carefully and use the units and context to help with calculations.\item \scriptsize Chef's Tips: Encourage students to check their work and use estimation to verify their answers.
\end{itemize}
\end{tcolorbox}

\end{document}
  