
\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, xcolor, geometry, enumitem, multicol, tcolorbox}

\definecolor{mainblue}{RGB}{0, 102, 204}
\geometry{a4paper, margin=1.2cm, top=1cm, bottom=3cm, footskip=1.2cm}

\begin{document}
\enlargethispage{2.5cm}

% Modern Header
\begin{tcolorbox}[colback=mainblue!5, colframe=mainblue, sharp corners, boxrule=0.5pt]
    \small \textbf{Unit:} Ὅ6 Unit 1: Ratio, Rate, Percentage \hfill \textbf{Name:} \rule{3cm}{0.4pt} \\
    \small \textbf{Topic:} Percent \hfill \textbf{Date:} \rule{2cm}{0.4pt} \\
    \centering \textbf{\large Quiz (Carolina Reaper)}
\end{tcolorbox}

\vspace{0.2cm}

% MCQ Section
\begin{multicols}{2}
\begin{enumerate}[label=\textbf{Q\arabic*.}, leftmargin=*, itemsep=6pt, parsep=0pt]

  \item \small A shipping company has $25$ trucks, and $15%$ of them are currently in maintenance. How many trucks are in maintenance?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item 2
    \item 3
    \item 4
    \item 3.75
    \item 5
  \end{enumerate}

  \item \small The traffic flow on a highway is $45%$ more than it was last year. If there were $200$ cars last year, how many are there now?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item 250
    \item 260
    \item 280
    \item 290
    \item 300
  \end{enumerate}

  \item \small A delivery company reduces its delivery time by $12%$. If the original delivery time was $50$ minutes, what is the new delivery time?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item 43.8
    \item 44
    \item 45
    \item 46
    \item 47
  \end{enumerate}

  \item \small A logistics company has a $25%$ increase in shipping costs. If the original cost was $$1000$, what is the new cost?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item $1200
    \item $1250
    \item $1300
    \item $1250
    \item $1300
  \end{enumerate}

  \item \small The number of flights at an airport increases by $18%$ from $250$ flights. How many flights are there now?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item 290
    \item 295
    \item 300
    \item 305
    \item 310
  \end{enumerate}

  \item \small A transportation company reduces its workforce by $8%$. If there were originally $400$ employees, how many are left?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item 360
    \item 365
    \item 368
    \item 370
    \item 372
  \end{enumerate}

  \item \small A package delivery company increases its delivery rate by $22%$. If the original delivery rate was $120$ packages per hour, what is the new rate?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item 140
    \item 145
    \item 146.4
    \item 150
    \item 155
  \end{enumerate}

  \item \small The cost of fuel for a truck increases by $5%$ from $$2.50$ per gallon. What is the new cost per gallon?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item $2.55
    \item $2.60
    \item $2.62
    \item $2.63
    \item $2.65
  \end{enumerate}

\end{enumerate}
\end{multicols}

\vspace{-0.2cm}
\hrule
\vspace{0.2cm}
\textbf{\small Open Ended Questions (FRQ)}
\begin{enumerate}[label=\textbf{Q\arabic*.}, start=9, itemsep=5pt, topsep=0pt]

  \item \small A shipping company has two types of trucks: large and small. The large trucks have a $15%$ increase in maintenance costs, while the small trucks have a $20%$ decrease. If the large trucks originally cost $$5000$ to maintain and the small trucks cost $$3000$, what is the total change in maintenance costs if there are $10$ large trucks and $15$ small trucks? \vspace{2cm}

  \item \small A logistics company is considering two shipping options. Option A has a $10%$ increase in shipping time, while Option B has a $12%$ decrease in shipping costs. If the original shipping time is $30$ hours and the original cost is $$1000$, which option is more cost-effective in terms of $$ per hour$? \vspace{2cm}

\end{enumerate}

\vfill

% Chef's Tips Footer
\begin{tcolorbox}[colback=blue!5, colframe=mainblue!50, title=\small \textbf{Chef's Tips}, fonttitle=\bfseries, bottom=1mm]
\begin{itemize}[noitemsep, topsep=2pt, leftmargin=0.5cm]
  \item \scriptsize Emphasize the importance of calculating percentages correctly\item \scriptsize Use real-world examples to illustrate percent increase and decrease\item \scriptsize Encourage students to check their answers for reasonableness
\end{itemize}
\end{tcolorbox}

\end{document}
  