
\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, xcolor, geometry, enumitem, multicol, tcolorbox}

\definecolor{mainblue}{RGB}{0, 102, 204}
\geometry{a4paper, margin=1.2cm, top=1cm, bottom=3cm, footskip=1.2cm}

\begin{document}
\enlargethispage{2.5cm}

% Modern Header
\begin{tcolorbox}[colback=mainblue!5, colframe=mainblue, sharp corners, boxrule=0.5pt]
    \small \textbf{Unit:} Unit 0: Foundations of Algebra \hfill \textbf{Name:} \rule{3cm}{0.4pt} \\
    \small \textbf{Topic:} Rational Numbers & Decimals \hfill \textbf{Date:} \rule{2cm}{0.4pt} \\
    \centering \textbf{\large Challenge (Habanero)}
\end{tcolorbox}

\vspace{0.2cm}

% MCQ Section
\begin{multicols}{2}
\begin{enumerate}[label=\textbf{Q\arabic*.}, leftmargin=*, itemsep=6pt, parsep=0pt]

  \item \small A gamer's high score is $45\%$ of the total points. If the total points are $1200$, what is the gamer's high score in points?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item $540$
    \item $600$
    \item $540$
    \item $480$
    \item $720$
  \end{enumerate}

  \item \small A new game has $3.5$ GB of free space. If it requires an update of $1.8$ GB, what fraction of the free space will be left after the update?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item $rac{3}{5}$
    \item $rac{1}{2}$
    \item $rac{4}{7}$
    \item $rac{7}{10}$
    \item $rac{9}{10}$
  \end{enumerate}

  \item \small To beat a level, a player must collect at least $75\%$ of the coins. If there are $480$ coins in total, how many coins must the player collect?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item $300$
    \item $320$
    \item $360$
    \item $380$
    \item $400$
  \end{enumerate}

  \item \small What is the decimal equivalent of $\frac{7}{8}$?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item $0.78$
    \item $0.80$
    \item $0.85$
    \item $0.875$
    \item $0.90$
  \end{enumerate}

  \item \small A game developer earns $2.5\%$ of the game's total revenue. If the game earns $$1,200,000$, how much does the developer earn?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item $$24,000$
    \item $$30,000$
    \item $$36,000$
    \item $$45,000$
    \item $$60,000$
  \end{enumerate}

  \item \small A player's score is $25\%$ more than their opponent's. If the opponent's score is $120$ points, what is the player's score?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item $140$
    \item $150$
    \item $160$
    \item $180$
    \item $200$
  \end{enumerate}

  \item \small A game requires $0.5$ GB of RAM to run. What fraction of $2$ GB is this?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item $rac{1}{2}$
    \item $rac{1}{3}$
    \item $rac{1}{4}$
    \item $rac{1}{5}$
    \item $rac{1}{6}$
  \end{enumerate}

  \item \small A gamer has $18.5$ hours of gaming time left. How many hours will they have left after playing for $2.5$ hours?
  \begin{enumerate}[label=(\Alph*), leftmargin=0.6cm, nosep, itemsep=2pt]
    \item $16$
    \item $16.5$
    \item $18$
    \item $20$
    \item $21$
  \end{enumerate}

\end{enumerate}
\end{multicols}

\vspace{-0.2cm}
\hrule
\vspace{0.2cm}
\textbf{\small Open Ended Questions (FRQ)}
\begin{enumerate}[label=\textbf{Q\arabic*.}, start=9, itemsep=5pt, topsep=0pt]

  \item \small A new update increases the game size by $15\%$. If the current size is $2.8$ GB, how much larger will the update be than the current size in GB? Show your work and express your answer as a decimal. \vspace{2cm}

  \item \small If a gamer earns $250$ points per hour and they have $3.75$ hours to play, how many points will they earn in total? Express the answer as a product of a whole number and a decimal. \vspace{2cm}

\end{enumerate}

\vfill

% Chef's Tips Footer
\begin{tcolorbox}[colback=blue!5, colframe=mainblue!50, title=\small \textbf{Chef's Tips}, fonttitle=\bfseries, bottom=1mm]
\begin{itemize}[noitemsep, topsep=2pt, leftmargin=0.5cm]
  \item \scriptsize Tip 1: Ensure students use exact decimal equivalents and fractions for calculations.\item \scriptsize Tip 2: Remind students to consider significant figures in their calculations.\item \scriptsize Tip 3: Encourage students to use visual aids like number lines for free response questions.
\end{itemize}
\end{tcolorbox}

\end{document}
  